---
title: "Exercise_01_Complete"
author: "Lucia Vilallonga"
date: "1/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Questions:

#### 1.
Evaluate the following:
   a.	ln(1)
   b.	ln(0)
   c.	ln(e)
   d.	ln(-5)
   e.	-ln(5)
   f.	ln(1/5)
   g.	How does R represent when the output of a function is not a number?

```{r}
log(1)
log(0)
log(exp(1))
log(-5)
-log(5)
log(1/5)
```
R prints 'NaN' (Not a Number) and gives a warning. 


#### 2.	
Why are we multiplying the results of the atan and atan2 functions by 180/pi? 

The functions atan() and atan2() in R return angles in Radians, which we can 
then convert to degrees by multiplying by 180/pi.

#### 3. 
How is the atan2 function different from the atan function? 

atan2() returns the angle between the x-axis and the vector from the origin to
the two input vectors x and y. atan(), on the other hand, returns the angle for
just one input vector. atan2(x, y) = atan(y/x).

#### 4.
What is the difference between log and log10?

log() returns the natural log (ln) of the input, whereas log10 returns the log
base-10. 

#### 5.

Given a right triangle with sides x = 5 and y = 13, calculate the length of the 
hypotenuse (show code)

```{r}
x = 5
y = 13
h = sqrt(x^2 + y^2)

h
```
#### 6.	

If a population starts with a density of 5 individuals/hectare and grows 
exponentially at a growth rate r=0.04/year, what is the size of the population 
in π years? (show code)

```{r}
pop_growth <- function(p, r, n) {
  res = p * ((1 + r)^n)
  
  return(res)
}

p = 5
r = 0.04
n = 10   # for example

pop_growth(p, r, n)
```
#### 7.	
Subtract the month you were born from the remainder left after you divide the year you were born by the day you were born (show code)

```{r}
funky_birth_dates <- function(month, year, day) {
  rem = year %% day
  res = rem - month
  
  return(res)
}

funky_birth_dates(3, 2000, 31)
```
### R Scripts

See `/home/lucia/bu/year4/semester2/EE509/labs/EE509/Exercise_01.R` for code.




